Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-04 WRITEUP/ms.tex

%mm2 [fiddled with tenses and plurals]
If constant column density (Larson's third relation) were truly a
fundamental property of molecular clouds,
% or the roughly linear relationship between $\rho$ and $R$ of MCCs.
%mm2 (i.e.,
   and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure,
one would expect a single point in the $\sigma_{\rm
  gas}^2/R$--$\Sigma$ relation at
% mm a given gas
    that
mass surface density $\Sigma$.
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental property of
molecular clouds
%mm2 [maybe this is excessive, but if we are discussing the issue it
% seems worth citing.]
     in agreement with \citet{Heyer09a}.
Previous studies suggest that the observed mass-size relation of molecular clouds
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of
column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).

%Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
%\citep{Larson81a, McKee07a}.
%Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
%which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
%the mass-size relation is also known as the constant column density relation and has been
%proposed as a fundamental property of molecular clouds on different physical scales.
%
%By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
%\begin{equation}
%A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
%\end{equation}
%Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
%\begin{equation}\label{eqn:constantcolumndensity}
%M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
%\end{equation}
%where we adopt $\mu = 2.5$ as the mean molecular weight.
%
%We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
%Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
%Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
%Further discussions on the interpretation of this is provided in \Sec{MR}.
%%
%%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
%%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however,
MCCs in the starburst phase span a wider range in gas surface density
(bottom panels of \Fig{larsons_single}) and have lower virial parameters.
That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby
ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.

@@

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds
corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher
$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$
 since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$
(see top panels of \Fig{alpha16-28}).
At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
%
%For instance, the cluster of points found at the lowest density threshold,
%occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28},
%are broken down into smaller MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
%that while the biggest MCCs are broken into smaller MCCs at higher $n_{\rm cut}$,
%MCCs identified at lower density in the outskirts of \flower
%typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
%%
%These MCCs are smaller in size, and thus, occupy the leftward in the top right panel.

%
The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in
nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%%
%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies,
spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
However, the sizes of MCCs are almost a factor of two smaller. This
%mm2 likely suggest
    suggests
that the sizes of \highz molecular gas structures reported in the literature
are
%mm2
   probably
limited by the spatial resolution.
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion
in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
%mm2
   This contrasts with \citet{Krumholz18}, who show that numerical models and analytic arguments point to
   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
   higher velocities likely being produced by Toomre instability driven radial inflow.

   The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs
%mm2 of \flower
are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

% different evolutionary stages
%mm2 [rearranged]
We do not find any major quantitative differences  (see \Fig{larsons_single}) in the MCCs of \flower with respect to those observed in the nearby Universe between its accreting and starburst phase, which are separated by $\simeq$300\,Myr. However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase. This is expected for \SF to proceed.

>>>>

If constant column density (Larson's third relation) were truly a
fundamental property of molecular clouds,
and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at that
mass surface density $\Sigma$.
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental property of
molecular clouds in agreement with \citet{Heyer09a}.
Previous studies suggest that the observed mass-size relation of molecular clouds
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of
column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however,
MCCs in the starburst phase span a wider range in gas surface density
(bottom panels of \Fig{larsons_single}) and have lower virial parameters.
That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby
ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%

@@

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds
corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher
$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$
 since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$
(see top panels of \Fig{alpha16-28}).
At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
%
The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in
nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies,
spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature
are probably limited by the spatial resolution.
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion
in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
%mm2
   This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to
   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
   higher velocities likely being produced by Toomre instability driven radial inflow.

   The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs
are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

We do not find any major quantitative differences (see \Fig{larsons_single}) in the MCCs of \flower with respect to those observed in the nearby Universe between its accreting and starburst phase, which are separated by $\simeq$300\,Myr. However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase. This is expected for \SF to proceed.
